%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Sriram}{Krishnaswamy}
{\urlstyle{same}\href{http://sriramkswamy.github.io}{sriramkswamy.github.io}|
	+1 (352) 872-8712	| \href{mailto:sriram.krish@ufl.edu}{sriram.krish@ufl.edu}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of Florida}
\descript{MS Mechanical Engineering}
\location{May 2016$^*$ | Gainesville, FL}
\location{Cum. GPA: 3.33 / 4.0}
\sectionsep

\subsection{BITS, Pilani}
\descript{MSc Chemistry}
\descript{BE Mechanical Engineering}
\location{May 2014 | Hyderabad, India}
\location{Cum. GPA: 7.54 / 10.0 \\
	Major GPA: 8.07 / 10.0}
\sectionsep

\subsection{DAV Boys}
\location{May 2009|  Chennai, India}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/sriramkswamy}{\bf sriramkswamy} \\
LinkedIn://  \href{https://www.linkedin.com/in/sriramkswamy}{\bf sriramkswamy} \\
SSL://  \href{http://web.mae.ufl.edu/~mrinalkumar/Research/research.html}{\bf Stochastic Systems Lab} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Experienced:}
C++ \textbullet{} Python \textbullet{} MATLAB \\
\location{Intermediate:}
Shell \textbullet{} \LaTeX\ \\
\location{Amateur:}
JavaScript \textbullet{} SQL \\
\sectionsep
\subsection{Libraries}
Boost \textbullet{} OpenMP \\
\sectionsep
\subsection{Softwares}
\location{Experienced:}
FLUENT \textbullet{} ANSYS \textbullet{} \\
\location{Amateur:}
SolidWorks \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Computational Fluid Dynamics \\
Uncertainity Quantification \\
Fluid Mechanics I \& II \\
Gas Turbines and Jet Engines \\
Compressible flow \\
Control Systems (\textbf{\textit{TA x1}}) \\
\sectionsep

\subsection{Undergraduate}
Numerical Methods \\
Applied Thermodynamics \\
Mechanics of Solids \\
CAD and FEA \\
Dynamics and Vibrations \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.66\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{EXPERIENCE}
\runsubsection{Stochastic Systems Laboratory}
\descript{| Student Assistant}
\location{May 2015 - Present | Gainesville, FL}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked with \textbf{\href{http://plaza.ufl.edu/yfsun/index.html}{Dr. Yifei Sun}} and
	\textbf{\href{http://web.mae.ufl.edu/~mrinalkumar/index.html}{Prof. Mrinal Kumar}} to create a Parallel
	Fokker-Planck equation solver based on CPD Tensor methods.
\item Simulated a 4 dimension 2 body problem using the
	\textbf{\href{http://www.boost.org/doc/libs/1_58_0/libs/numeric/ublas/doc}{Boost uBLAS library}}
\item Extended the Tensor CPD method for Lorenz parameterized models used in wind forecasting
\end{tightemize}
% \location{Nov 2014 – April 2015 | Gainesville, FL}
% \begin{tightemize}
% \item Predicted the optimal cost and risks for a multi-reservoir system using Chance-constrained Optimization
% \end{tightemize}
\sectionsep

\runsubsection{Thermal Turbomachines Laboratory}
\descript{| Project Assistant}
\location{June 2013 – May 2014 | Chennai, India}
\begin{tightemize}
\item Automated the CFD analysis of airfoils using Python and Scheme.
\item Implemented intelligent data interpretation and post-processing.
\item Used it analyze the effects of Synthetic jet active flow control in airfoils.
\item Collaborated with Shubham Jain to analyze the effects of Gurney Flap.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{CanSat 2013}
\descript{| Team Leader }
\location{Nov 2012 – June 2013 | Abilene, TX}
\begin{tightemize}
\item Led Team Varuna - the first team from BITS, Pilani to a successful launch.
\item Scored 97.15\% in the Critical Design Review
\item Raised a sponsorship of \$1,500 and presented the design to the Director of ISRO
(Indian Space Research Organization)
\end{tightemize}
\sectionsep

\runsubsection{Computational Fluid Dynamics}
\descript{| Independent Projects }
\location{Jan 2016 – Present | Gainesville, FL}
\begin{tightemize}
\item Python based solver for solving 2D Heat equation.
\item Based on the \textbf{\href{https://itunes.apple.com/us/itunes-u/computational-fluid-dynamics/id452560554?mt=10}
        {CFD course}} by \textbf{\href{http://lorenabarba.com}{Prof. Lorena Barba}}
\end{tightemize}
\location{Sep 2015 – Dec 2015 | Gainesville, FL}
\begin{tightemize}
\item Central difference scheme to solve the diffusion equation
\item First and second order upwind schemes to solve the convection-diffusion equation.
\item AB3 and RK4 methods for \textbf{\href{https://github.com/sriramkswamy/CFDEGM6342.git}{1D and 2D cases}} of the Burgers equation
\end{tightemize}
% \location{May 2012 – July 2012 | Hyderabad, India}
% \begin{tightemize}
% \item Modelled NACA4421 airfoil using ANSYS and ICEM CFD for a term project.
% \item Analyzed the flow separation spectrum to identify the most effective point for flow control.
% \end{tightemize}
\sectionsep

\runsubsection{Hovercraft}
\descript{| Team Leader }
\location{Jan 2012 – May 2012 | Hyderabad, India}
\begin{tightemize}
\item Designed, analysed and fabricated a single seater Hovercraft capable of lifting a person of 80 kgs
\item Raised a sponsorship of INR 15,000 for the equipment and testing as the treasurer of collegiate SAE Chapter
\item Successfully completed manned tests for levitation
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Selected Publications}
\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
\bibliographystyle{abbrv}
\bibliography{publications}
\nocite{*}

\end{minipage}
\end{document}
